MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-07-19 main/MSstatsPTM_Main.tex
Cosmetics

For example, in the simple case of \figref{data-structure} with $J=2$ conditions, where $\hat{\sigma}^2_{PTM}$ and $\hat{\sigma}^2_{protein}$ are the estimates of the error variance for the PTM and protein model described in \eqref{msstats_model}, the standard error would be calculated as

\begin{eqnarray}
& \widehat{SE}(\hat{\Delta}_{adj}) = \sqrt{\widehat{SE}(\hat{\Delta}_{PTM})^2 + \widehat{SE}(\hat{\Delta}_{protein})^2} = &\\ 
& \sqrt{\frac{1}{J}\hat{\sigma}^2_{PTM} + \frac{1}{J}\hat{\sigma}^2_{protein}} = \sqrt{\frac{2}{J}(\hat{\sigma}^2_{PTM} + \hat{\sigma}^2_{protein})} = \sqrt{\hat{\sigma}^2_{PTM} + \hat{\sigma}^2_{protein}} & \nonumber
\label{eq:se_calc}
\end{eqnarray}

>>>>

For example, in the simple case of \figref{data-structure} with $J=2$ conditions, where $\hat{\sigma}^2_{PTM}$ and $\hat{\sigma}^2_{protein}$ are the estimates of the error variance for the PTM and protein model described in \eqref{msstats_model}, the standard error would be calculated as
\begin{eqnarray}
 \widehat{SE}(\hat{\Delta}_{adj}) &=& \sqrt{\widehat{SE}(\hat{\Delta}_{PTM})^2 + \widehat{SE}(\hat{\Delta}_{protein})^2} \\ 
&=& \sqrt{\frac{1}{J}\hat{\sigma}^2_{PTM} + \frac{1}{J}\hat{\sigma}^2_{protein}} = \sqrt{\frac{2}{J}(\hat{\sigma}^2_{PTM} + \hat{\sigma}^2_{protein})} = \sqrt{\hat{\sigma}^2_{PTM} + \hat{\sigma}^2_{protein}} \nonumber
\label{eq:se_calc}
\end{eqnarray}
